|

### 2020-09-08 paper.Rmd
Some rewriting of pdfsense example.

Data were obtained from CT14HERA2 parton distribution function fits as used in [reference]. There are 28 directions in the parameter
space of parton distribution function fit, each point in the variables labelled X1-X56 indicate moving 1 standard devation from the 'best'
(maximum likelihood estimate) fit of the function in either positive or negative direction. Each observation has all predictions of the corresponding measurement from an experiment. Each point
is colored according to different underlying processes in the experiment. The goal of the analysis is to identify the trajectory of the experiments along the parameter space corresponding to a given process.

Following the processing described in [@ ursula's paper ], we tour the first 6 principal components, rescaled to have zero mean and unit variance. In figure \ref{fig:pdfsense} we see that using the sage display with $R = 10$ (figure \ref{fig:pdfsense}, right), expands the center of the distribution compared to the regular tour display  (figure \ref{fig:pdfsense}, left), while maintaining the global structure of the data (different physical process are orthogonal in the paramater space). Here using the sage display allows us to see more detail at the center, and identifies parameters that are at intersection of all three physical processes.

>>>>

Data were obtained from CT14HERA2 parton distribution function fits and describe the sensitivity of fit parameters to experimental measurements [@Wang:2018heo]. There are 28 parameters, and varying one at a time to move $\pm 1 \sigma$ away from the 'best fit point' (maximum likelihood estimate) provides our input variables, labelled X1-X56. Each observation corresponds to the fit prediction for these 56 parameter combination for a single physical observable. Points are grouped based on the underlying process in the experiment, which is mapped to color in the following. With the analysis of the distribution along these variables X1-X56 we can understand to what extent each experimental measurement provides complementary information for the global fit, e.g. orthogonality between the three groups or the identification of outlying points which are considered as important for future fits, see discussion in @Cook:2018mvr.

Following the processing described there, we tour the first 6 principal components, rescaled to have zero mean and unit variance. In figure \ref{fig:pdfsense} we see that using the sage display with $R = 10$ (figure \ref{fig:pdfsense}, right), expands the center of the distribution compared to the regular tour display  (figure \ref{fig:pdfsense}, left), while maintaining the global structure of the data (different physical process are orthogonal in the paramater space). Here using the sage display allows us to see more detail at the center, and identifies parameters that are at intersection of all three physical processes.

The particular structure of this distribution, with some clusters extending linearly away from the center and a set of outlying points, results in poor use of the plotting space, and high level of clustering near the center. For example, focussing on the blue cluster, we can see that it extends out along different directions, but it can be challenging to observe how the point move under the tour rotation, as overplotting becomes an issue when points move through the center. Here, the new display has a clear advantage, as illustrated with the selected views in Fig XXX.
